The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-07-23 article.tex
Added code examples for SMILES

  \subsubsection*{SMILES parser}

  The SMILES parsing has been replaced code in the external Beam project~\cite{Beam}.
  This BSD-licensed SMILES parser is a complete implementation of the SMILES
  and OpenSMILES specifications by one of the authors, and is independent of
  the CDK library. The SmilesParser API uses this library underneath, and the
  Beam API is hidden by this class.

>>>>

  \subsubsection*{SMILES parser and generator}

  The SMILES parsing has been replaced code in the external Beam project~\cite{Beam}.
  This BSD-licensed SMILES parser is a complete implementation of the SMILES
  and OpenSMILES (\url{http://opensmiles.org/}) specifications by one of the
  authors (including stereochemistry), and is independent of
  the CDK library. The SmilesParser API uses this library underneath, and the
  Beam API is hidden by this class. The most significant change here is that
  the SMILES parser now automatically locates the positions of double bonds,
  but this can be turned off:

\begin{verbatim}
  SmilesParser parser = new SmilesParser(
    SilentChemObjectBuilder.getInstance()
  );
  parser.kekulise(false);
  mol = parser.parseSmiles(smi);
\end{verbatim}

  The SMILES generation API has also been simplified and made more flexible.
  Creating unique SMILES or aromatic SMILES is now done by first creating a
  SMILES generator instance which can make generic or unique SMILES, and with
  or without simplifying aromatic rings using the lower case element symbols
  for the organic subset. This generator can then be repeatedly called:

\begin{verbatim}
  uniqueGenerator = SmilesGenerator.unique()
  aromaticGenerator = SmilesGenerator.generic().aromatic()
  smiles = uniqueGenerator.createSMILES(mol)
  smiles2 = atomaticGenerator.createSMILES(mol)
\end{verbatim}
